Structured Versus Decorated Cospans

### 2020-11-23 cospans.tex
going through 2.1

\begin{thm}\label{thm:decorated_cospans}
Let $\A$ be a category with finite colimits and $F \maps \A \to \Cat$ a lax monoidal pseudofunctor. Then there exists a double category $F\lCsp$ in which
\begin{itemize}
\item an object is an object of $\A$,
\item a vertical 1-morphism is a morphism of $\A$,
\item a horizontal 1-cell is an $F$\define{-decorated cospan}: that is, 
a cospan in $\A$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$m$};
\node (C) at (2,0) {$b,$};
%\node (D) at (2.6,0) {$x \in F(m))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
together with a \define{decoration} $x \in F(m)$,
\item a 2-morphism is a \define{map of} $F$\define{-decorated cospans}: that is, 
a map of cospans in $\A$:
\begin{displaymath}
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a'$};
\node (B) at (1,0.5) {$m$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b'$};
\node (D) at (1,-0.5) {$m'$};
\node (E) at (3,0.5) {$x \in F(m)$};
\node (F) at (3,-0.5) {$x' \in F(m')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[right]{$g$} (C')
(A') edge node[above] {$i'$} (D)
(C') edge node[above] {$o'$} (D)
(B) edge node [left] {$h$} (D);
\end{tikzpicture}
\end{displaymath}
together with a \define{decoration morphism} $\tau \maps F(h)(x) \to x'$ in $F(m')$.
\end{itemize}
\end{thm}

\begin{proof}
The definition of double category may be found in Definition \ref{defn:double_category}. To show that the pseudofunctor $F$ in the theorem statement induces a double category $F\lCsp$, we must first define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$, the unit functor $U \colon F\lCsp_0 \to F\lCsp_1$ and the composition functor $\odot$ which says how to compose two composable horizontal 1-cells or two composable 2-morphisms horizontally: $$\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1.$$

@@

 %\noindent
%\textbf{In progress...}
%we get a natural isomorphism $a_{M_1,M_2,M_3} \maps (M_1 \odot M_2) \odot M_3 \to M_1 \odot (M_2 \odot M_3)$ which is a globular 2-morphism given by a map of cospans $(\id_{a_1},\sigma,\id_{a_4})$:
%with the decorations on the cospan's apices given by:
%$$ (x \odot y) \odot z \mapseqq 1 \xrightarrow{\zeta_1} F(m_1+_{b} m_2) \times F(m_3) \xrightarrow{\phi_{m_1+_{b} m_2, m_3}} F((m_1+_{b}m_2) +m_3) \xrightarrow{F(j_{m_1+_{b} m_2,m_3})} F((m_1+_{b} m_2)+_{c} m_3)$$ $$\zeta_1 = (1 \times z) \rho^{-1} F(j_{m_1,m_2}) \phi_{m_1,m_2} (x \times y) \lambda^{-1}$$
%and
%$$ x \odot (y \odot z) \mapseqq 1 \xrightarrow{\zeta_2} F(m_1) \times F(m_2 +_{c} m_3) \xrightarrow{\phi_{m_1, m_2 +_{c} m_3}} F(m_1+(m_2 +_{c} m_3)) \xrightarrow{F(j_{m_1,m_2 +_{c} m_3})} F(m_1+_{b} (m_2+_{c} m_3))$$ $$\zeta_2 = (x \times 1) \lambda^{-1} F(j_{m_2,m_3}) \phi_{m_2,m_3} (y \odot z) \lambda^{-1}$$
%together with the isomorphism $\tau_\sigma \maps F(\sigma)((x \odot y) \odot z) \to x \odot (y \odot z)$. Note that the map $\sigma \maps (m_1+_{b} m_2)+_{c}m_3 \to m_1+_{b}(m_2+_{c}m_3)$ is the universal map between two colimits of the same diagram. 
%\noindent
%We also have left and right unitors where given a horizontal 1-cell $M$:
%\node (B) at (1,0) {$m$};

@@

%(C) edge node[above]{$o$} (B);
%if we, say, compose with the identity horizontal 1-cell of $b$ on the right:
%\node (B) at (1,0) {$m$};
%\node (D) at (1,-0.5) {$x \in F(m)$};
%\node (E) at (3,0) {$b$};
%\node (F) at (4,0) {$b$};
%\node (G) at (5,0) {$b$};
%\node (H) at (4,-0.5) {$!_{b} \in F(b)$};
%(E) edge node[above]{$1$} (F)
%(G) edge node[above]{$1$} (F);
%where $!_{b} = F(!)  \phi \maps 1 \to F(b)$ is the trivial decoration on $b$, composing these then gives:
%\node (B) at (1,0) {$m+_{b} b$};
%\node (D) at (3.5,0) {$x \odot !_b \in F(m +_{b} b)$};
%(A) edge node[above]{$j \psi_m i$} (B)
%(C) edge node[above]{$j \psi_{b}$} (B);
%where $\psi_m \maps m \to m+b$ is the natural map into the coproduct and likewise for $\psi_{b}$ and $j \maps m+b \to m+_{b} b$ is the natural map from the coproduct to the pushout. The decoration $x \odot !_b \maps 1 \to F(m+_{b} b)$ is given by: $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times !_{b}} F(m) \times F(b) \xrightarrow{\phi_{m,b}} F(m+b) \xrightarrow{F(j_{m,b})} F(m+_{b} b).$$ We then have that the right unitor $R \maps M \odot 1_{b} \xrightarrow{\sim} M$ is given by the globular 2-morphism $(\id_{a},r,\id_{b})$ from the above composite to $M$:
%\node (A') at (0,-0.5) {$a$};
%\node (B) at (1.5,0.5) {$m+_{b} b$};
%\node (C) at (3,0.5) {$b$};
%\node (C') at (3,-0.5) {$b$};
%\node (D) at (1.5,-0.5) {$m$};
%\node (E) at (4.5,0.5) {$x \odot !_b \in F(m+_{b} b)$};
%\node (F) at (4.5,-0.5) {$x \in F(m)$};
%(A) edge node[above]{$j \psi_m i$} (B)
%(C) edge node[above]{$j \psi_{b}$} (B)
%(A) edge node[left]{$\id_{a}$} (A')
%(C) edge node[right]{$\id_{b}$} (C')
%(A') edge node [above]{$i$} (D)
%(C') edge node [above]{$o$} (D)
%(B) edge node [left] {$r$} (D);
%where $r \maps m+_{b} b \xrightarrow{\sim} m$ is a universal map together with the isomorphism $\tau_r \maps F(r)(x \odot !_b) \to x$. The left unitor is similar. The source and target functor applied to the left and right unitors and associators yield identities, and the left and right unitors together with the associator satisfy the standard pentagon and triangle identities of a monoidal category or bicategory. Finally, for the interchange law, given four 2-morphisms $\alpha, \beta, \alpha'$ and $\beta'$:
%if we first compose horizontally we obtain:
%\node (B) at (1.5,0.5) {$m+_{b} n$};
%\node (C) at (3,0.5) {$c$};
%\node (C') at (3,-0.5) {$c'$};
%\node (D) at (1.5,-0.5) {$m' +_{b'} n'$};
%\node (E) at (4.5,0.5) {$x \odot y \in F(m+_{b} n)$};
%\node (F) at (4.5,-0.5) {$x' \odot y' \in F(m' +_{b'} n')$};
%\node (G) at (1.5,-1) {$\tau_{\alpha \odot \beta} \maps F(h_1 +_g h_2)(x \odot y) \to x' \odot y'$};
%\node (A'') at (0,-1.5) {$a'$};
%\node (A''') at (0,-2.5) {$a''$};
%\node (B'') at (1.5,-1.5) {$m' +_{b\prime} n'$};
%\node (C'') at (3,-1.5) {$c'$};
%\node (C''') at (3,-2.5) {$c''$};
%\node (D'') at (1.5,-2.5) {$m'' +_{b''} n''$};
%\node (E'') at (4.5,-1.5) {$x' \odot y' \in F(m'+_{b'} n')$};
%\node (F'') at (4.5,-2.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
%\node (G'') at (1.5,-3) {$\tau_{\alpha' \odot \beta'} \maps F(h_1' +_{g'} h_2')(x' \odot y') \to x'' \odot y''.$};
%(A) edge node[above]{$j \psi_{m} i_1$} (B)
%(C) edge node[above]{$j \psi_{n} o_2$} (B)
%(C) edge node[right]{$k$} (C')
%(A') edge node [above]{$j \psi_{m'} i_1'$} (D)
%(C') edge node [above]{$j \psi_{n'} o_2'$} (D)
%(B) edge node [left] {$h_1 +_g h_2$} (D)
%(A'') edge node[above]{$j \psi_{m'} i_1'$} (B'')
%(C'') edge node[above]{$j \psi_{n'} o_2'$} (B'')
%(A'') edge node[left]{$f'$} (A''')
%(C'') edge node[right]{$k'$} (C''')
%(A''') edge node [above]{$j \psi_{m''} i_1''$} (D'')
%(C''') edge node [above]{$j \psi_{n''} o_2''$} (D'')
%(B'') edge node [left] {$h_1' +_{g'} h_2'$} (D'');
%To obtain the morphism of decorations for a horizontal composite, we have as initial data:
%\node (A) at (4,0) {$\tau_\alpha \Swarrow$};
%\node (D) at (3,0) {$1$};
%\node (E) at (4.5,0.5) {$F(m)$};
%\node (E') at (4.5,-0.5) {$F(m')$};
%\node (A') at (6.5,0) {$\tau_\beta \Swarrow$};
%\node (D') at (5.5,0) {$1$};
%\node (E'') at (7,0.5) {$F(n)$};
%\node (E''') at (7,-0.5) {$F(n')$};
%(D) edge node [above] {$x$} (E)
%(D) edge node [below] {$x'$} (E')
%(E) edge node [right] {$F(h_1)$} (E')
%(D') edge node [above] {$y$} (E'')
%(D') edge node [below] {$y'$} (E''')
%(E'') edge node [right] {$F(h_2)$} (E''');
%These two 2-morphisms $\tau_\alpha$ and $\tau_\beta$ are two 2-morphisms in the monoidal 2-category $(\Cat,\times,1)$ and so we can tensor them which results in:
%Returning to the interchange law, composing the two horizontal compositions above vertically then results in:
%\node (A') at (0,-0.5) {$a''$};
%\node (B) at (2,0.5) {$m+_{b} n$};
%\node (C) at (4,0.5) {$c$};
%\node (C') at (4,-0.5) {$c''$};
%\node (D) at (2,-0.5) {$m'' +_{b''} n''$};
%\node (E) at (5.5,0.5) {$x \odot y \in F(m+_{b} n)$};
%\node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
%\node (G) at (2,-1) {$\tau_{(a' \odot \beta')(\alpha \odot \beta)} \maps F((h_1' +_{g'} h_2')(h_1 +_g h_2))(x \odot y) \to x'' \odot y''.$};
%(A) edge node[above]{$j \psi_{m} i_1$} (B)
%(C) edge node[above]{$j \psi_{n} o_2$} (B)
%(A) edge node[left]{$f' f$} (A')
%(C) edge node[right]{$k' k$} (C')
%(A') edge node [above]{$j \psi_{m''} i_1''$} (D)
%(C') edge node [above]{$j \psi_{n''} o_2''$} (D)
%(B) edge node [left] {$(h_1' +_{g'} h_2')(h_1 +_g h_2)$} (D);
%The vertical composite of two morphisms of decorations is straightforward. On the other hand, if we first compose vertically we obtain:
%\node (A') at (0,-0.5) {$a''$};
%\node (B) at (1,0.5) {$m$};
%\node (C') at (2,-0.5) {$b''$};
%\node (D) at (1,-0.5) {$m''$};
%\node (E) at (3,0.5) {$x \in F(m)$};
%\node (F) at (3,-0.5) {$x'' \in F(m'')$};
%\node (G) at (4,0.5) {$b$};
%\node (H) at (5,0.5) {$n$};
%\node (I) at (6,0.5) {$c$};
%\node (G') at (4,-0.5) {$b''$};
%\node (H') at (5,-0.5) {$n''$};
%\node (I') at (6,-0.5) {$c''$};
%\node (J) at (7,0.5) {$y \in F(n)$};
%\node (K) at (7,-0.5) {$y'' \in F(n'')$};
%\node (L) at (1,-1) {$\tau_{\alpha' \alpha} \maps F(h_1' h_1)(x) \to x''$};
%\node (M) at (5,-1) {$\tau_{\beta' \beta} \maps F(h_2' h_2)(y) \to y''$};
%(A) edge node[above]{$i_1$} (B)
%(C) edge node[above]{$o_1$} (B)
%(A) edge node[left]{$f' f$} (A')
%(C) edge node[right]{$g' g$} (C')
%(A') edge node[above] {$i_1''$} (D)
%(C') edge node[above] {$o_1''$} (D)
%(B) edge node [left] {$h_1' h_1$} (D)
%(G) edge node [above] {$i_2$} (H)
%(G) edge node [left] {$g' g$} (G')
%(H) edge node [left] {$h_2' h_2$} (H')
%(G') edge node [above] {$i_2''$} (H')
%(I) edge node [above] {$o_2$} (H)
%(I) edge node [right] {$k' k$} (I')
%(I') edge node [above] {$o_2''$} (H');
%and then composing horizontally results in:
%\node (A') at (0,-0.5) {$a''$};
%\node (B) at (2,0.5) {$m+_{b} n$};
%\node (C) at (4,0.5) {$c$};
%\node (C') at (4,-0.5) {$c''$};
%\node (D) at (2,-0.5) {$m'' +_{b''} n''$};
%\node (E) at (5.5,0.5) {$x \odot y \in F(m+_{b} n)$};
%\node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
%\node (G) at (2,-1) {$\tau_{(\alpha' \alpha) \odot (\beta' \beta)} \maps F((h_1' h_1)+_{g' g} (h_2' h_2))(x \odot y) \to x'' \odot y''.$};
%(A) edge node[above]{$j \psi_{m} i_1$} (B)
%(C) edge node[above]{$j \psi_{n} o_2$} (B)
%(A) edge node[left]{$f' f$} (A')
%(C) edge node[right]{$k' k$} (C')
%(A') edge node [above]{$j \psi_{m''} i_1''$} (D)
%(C') edge node [above]{$j \psi_{n''} o_2''$} (D)
%(B) edge node [left] {$(h_1' h_1) +_{g' g} (h_2' h_2)$} (D);
%The decorations of 
%\node (B) at (2,0) {$F(c) \times F(e)$};
%\node (C) at (4,0) {$F(c+e)$};
%\node (D) at (4,-1) {$F(c+_b e)$};
%\node (E) at (4,-2) {$F(c'' +_{b''} e'')$};
%\node (F) at (0,-1) {$F(c) \times F(e)$};
%\node (G) at (0,-2) {$F(c'') \times F(e'')$};
%\node (H) at (2,-2) {$F(c'' + e'')$};
%(A) edge node [above]{$d_1 \times d_2$} (B)
%(B) edge node [above] {$\phi_{c,e}$} (C)
%(C) edge node [right]{$F(j_{c,e})$} (D)
%(D) edge node [right] {$F((h_1' +_{g'} h_2')(h_1 +_g h_2))$} (E)
%(A) edge node [left] {$d_1 \times d_2$} (F)
%(F) edge node [left] {$F((h_1' h_1) \times (h_2' h_2))$} (G)
%(G) edge node [above] {$\phi_{c'',e''}$} (H)
%(H) edge node [above] {$F(j_{c'',e''})$} (E);
%As is usual concerning the interchange law of double categories of this nature, only the `interior' of the two composites appears different, but the two morphisms $(h_1' +_{g'} h_2')(h_1 +_g h_2) \maps m+_{b} n \to m'' +_{b''} n''$ and $(h_1' h_1) +_{g' g} (h_2' h_2) \maps m+_{b} n \to m'' +_{b''}n''$ are the same universal map realized in two different ways. The two morphisms of decorations $\tau_{(\alpha' \odot \beta')(\alpha \odot \beta)}$ and $\tau_{(\alpha' \alpha) \odot (\beta' \beta)}$ are obtained as two different compositions of four 2-morphisms in $\Cat$, namely horizontally then vertically and vertically then horizontally. As $\Cat$ is a 2-category, the interchange law for these 2-morphisms already holds, and as a result, the morphisms $$\tau_{(\alpha' \odot \beta')(\alpha \odot \beta)} \maps F((h_1' +_{g'} h_2')(h_1 +_g h_2))(x \odot y) \to x'' \odot y''$$ and $$\tau_{(\alpha' \alpha)\odot(\beta' \beta)} \maps F((h_1' h_1)+_{g' g} (h_2' h_2))(x \odot y) \to x'' \odot y''$$ are also the same. Thus the interchange law for 2-morphisms holds and $F\mathbb{C}$sp is a double category.

>>>>

\begin{thm}\label{thm:decorated_cospans}
Let $\A$ be a category with finite colimits and $F \maps \A \to \Cat$ a lax monoidal pseudofunctor. Then there exists a double category $F\lCsp$ in which
\begin{itemize}
\item an object is an object of $\A$,
\item a vertical 1-morphism is a morphism of $\A$,
\item a horizontal 1-cell is an $F$\define{-decorated cospan}, that is, 
a cospan in $\A$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$m$};
\node (C) at (2,0) {$b,$};
%\node (D) at (2.6,0) {$x \in F(m))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
together with a \define{decoration} $x \in F(m)$,
\item a 2-morphism is a \define{map of} $F$\define{-decorated cospans}, that is, 
a map of cospans in $\A$:
\begin{equation}\label{eq:mapofdec}
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a'$};
\node (B) at (1,0.5) {$m$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b'$};
\node (D) at (1,-0.5) {$m'$};
\node (E) at (3,0.5) {$x \in F(m)$};
\node (F) at (3,-0.5) {$x' \in F(m')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[right]{$g$} (C')
(A') edge node[above] {$i'$} (D)
(C') edge node[above] {$o'$} (D)
(B) edge node [left] {$h$} (D);
\end{tikzpicture}
\end{equation}
together with a \define{decoration morphism} $\tau \maps F(h)(x) \to x'$ in $F(m')$.
\end{itemize}
\end{thm}

\begin{proof}
According to \cref{defn:double_category}, we will define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$, the composition functor 
$\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1$ and the unit functor $U \colon F\lCsp_0 \to F\lCsp_1$.

The category of objects $F\lCsp_0$ is simply the category $\A$, whereas $F$-decorated cospans and maps between them form the category of arrows $F\lCsp_1$. For example, the (vertical) composition of two $F$-decorated cospans maps is 
\begin{displaymath}
 \begin{tikzcd}
a\ar[r,"i"]\ar[d,"f"'] & m\ar[d,"h"] & b\ar[l,"o"]\ar[d,"g"]  & x\in F(m) \\
a'\ar[r,"{i'}"]\ar[d,"{f'}"] & m'\ar[d,"{h'}"] & b'\ar[l,"{o'}"']\ar[d,"{g'}"] & x'\in F(m') \\
a''\ar[r,"{i''}"'] & m'' & b''\ar[l,"{o''}"'] & x''\in F(m'')
 \end{tikzcd}\;=\;
 \begin{tikzcd}[column sep=.4in]
a\ar[r,"i"]\ar[dd,"{f'f}"'] & m\ar[dd,"{h'h}"] & b\ar[l,"o"]\ar[dd,"{g'g}"]  & x\in F(m) \\
\hole \\
a''\ar[r,"{i''}"] & m'' & b''\ar[l,"{o''}"'] & x''\in F(m'')  
 \end{tikzcd}
\end{displaymath}
where if $\tau \colon F(h)(x) \to x'$ and $\tau' \colon F(h')(x') \to x''$ are the decoration morphisms, $\tau' F(\tau) \colon F(h'h)(x) \to x''$ is the composite one.
The source and target functors map an $F$-decorated cospan to the source and target of the cospan and a map of decorated cospans \cref{eq:mapofdec} to $f$ and $g$ respectively.

The unit functor $U \maps F\lCsp_0 \to F\lCsp_1$ is defined on objects as: 
\begin{equation}\label{eq:UFCsp}
\begin{tikzpicture}[scale=1.5]
\node (E) at (-1,0) {$a$};
\node (F) at (-.5,0) {$\mapsto$};
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$a$};
\node (C) at (2,0) {$a$};
\node (D) at (3,0) {$\bot_a \in F(a)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B);
\end{tikzpicture}
\end{equation}
where $\bot_a \in F(a)$ is the \define{trivial decoration} on $a$ given by the composite of the unique map $F(!) \maps F(0) \to F(a)$ and the morphism $\phi \maps 1 \to F(0)$  which comes from $F \maps \A \to \Cat$ being lax monoidal.  For morphisms, the functor $U$ is defined as:
\[
\begin{tikzpicture}[scale=1.5]
\node (G) at (-1,0.5) {$a$};
\node (G') at (-1,-0.5) {$a'$};
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a'$};
\node (B) at (1,0.5) {$a$};
\node (C) at (2,0.5) {$a$};
\node (C') at (2,-0.5) {$a'$};
\node (D) at (1,-0.5) {$a'$};
\node (E) at (3,0.5) {$\bot_a \in F(a)$};
\node (F) at (3,-0.5) {$\bot_{a'} \in F(a')$};
\node (H) at (-0.5,0) {$\mapsto$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[right]{$f$} (C')
(A') edge node[above] {$1$} (D)
(C') edge node[above] {$1$} (D)
(B) edge node [left] {$f$} (D)
(G) edge node [left] {$f$} (G');
\end{tikzpicture}
\]
together with the morphism $\tau_{\bot_f} = F(f) F(!) \phi \maps 1 \to F(a')$.

@@

 The definition of double category may be found in Definition \ref{defn:double_category}. To show that the pseudofunctor $F$ in the theorem statement induces a double category $F\lCsp$, we must first define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$, the unit functor $U \colon F\lCsp_0 \to F\lCsp_1$ and the composition functor $\odot$ which says how to compose two composable horizontal 1-cells or two composable 2-morphisms horizontally: $$\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1.$$

@@
